---
title: "Data Visualisations Exercises (3.3.4)"
author: "Mohammed Shaahid Khan"

output: html_document
---

```{r}
library(ggplot2)
ggplot2::mpg

```
## Q1) Run ggplot(data = mpg). What do you see?
  
  A blank canvas that requires the need for geompoints or 'layers'
  this is done by calling the function
---
  $$ggplot(data = subset) +
    GEOM Function(mapping = aes(x = xlabel,y = ylabel))$$
---

```{r}

ggplot(data=mpg)

```
---
## Q2) How many rows are in mpg? How many columns?

R has a calling function that provides these details shown below
$$nrows(mpg),ncol(mpg)$$

```{r}
nrow(mpg) 
ncol(mpg)
```
---
## Q3) What does the drv variable describe? Read the help for ?mpg to find out.

calling the ?mpg gives the description of all relevant variavles for mpg. drv variable states that it represents type of drive train, (f= front wheel drive, r= rear wheel drive, 4 = 4wd)

```{r}
?mpg
```
---
## Q4) Make a scatterplot of hwy vs cyl

To note, hwy is highway miles and cyl is numer of cylinders. it seems that the lower cylinder in a vehicle, the general hwy limits are also lower compared to vehicles with a higher cylinder count. However, there is a big overlap with 4,6, and 8 cylinder vehicles. We can assume that the highway milage per gallon is generally $$22<hwy<26$$. For 4 cyclinder vehicles, the maximum is significantly higher.

```{r}

ggplot(mpg) +
  geom_point( mapping = aes(x = hwy, y = cyl))

```
---
## Q5) What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

The plot is not useful because the scatterplot data has no negative or positive pattern when looking at these two features. Also, the data does not give a direct intepretation on fuel consumptopn but rather how vehicles can vary with the type of drive chain. this added to a a matrix scatterplot may prove more useful.


```{r}
ggplot(mpg) +
  geom_point(mapping = aes(x=class,y=drv))
```